---
title: "midterm 1"
author: "Nora Garrity- ngarri3"
date: "10/14/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.
```{r}
gpa.data = c(3.39, 3.30, 2.81, 3.03, 3.44, 3.07, 3.00, 3.43, 3.36, 3.13, 3.12, 2.74, 2.76, 2.88, 3.96)

D = length(gpa.data)
Tn = median(gpa.data)
Tn_hat = rep(0, D)

for(d in 1:D) {
  X_hat = gpa.data[sample(length(gpa.data), D, replace = TRUE)]
  Tn_hat[d] = median(X_hat)
}
seboot = sqrt(var(Tn_hat)) #textbook pg. 31
seboot

Tn - seboot*qnorm(1-.1/2)
Tn + seboot*qnorm(1-.1/2)
```
The plug in estimate of the median is 3.12. The standard error of the median is 0.1543651. The procedure is to repeatedly test the same data some amount of times in order to simulate many random tests, and then take my data values from that. The confidence interval is [2.866092, 3.373908]


2.
```{r}
n= length(gpa.data)
Tn = median(gpa.data)
Ti = rep(0, n)

for(i in 1:n) {
  Ti[i] = median(gpa.data[-i])
}

jackknife = (n - 1)*((1/n)*sum(Ti) - Tn)

estimate_median = Tn - jackknife
estimate_median

pseudo = n*Tn - (n-1)*Ti

var_jackknife = (1/n)*(1/(n - 1))*sum((pseudo - (1/n)*sum(pseudo))**2)
se_jackknife = sqrt(var_jackknife)
se_jackknife

estimate_median - se_jackknife*qnorm(1-0.1/2)
estimate_median + se_jackknife*qnorm(1-0.1/2)

```
The plug in estimate of the median is 3.269333. The standard error of the median is .05501919. The confidence interval is [3.178835, 3.359832]

3.
```{r}
h = 0.25
boxcar_kernel = function(x) { 
  if(abs(x) <= 1) {
    return(0.5)
  } else {
    return(0)
  }
}

kernel_density_estimator <- function(x) {
kern = rep(0, n)
for(i in 1:n) {
kern[i] = boxcar_kernel((x - gpa.data[i])/h)/h  
}
return((1/n)*sum(kern))
}

kernel_density_estimator(3)
```
The kernel density estimate is 1.066667

5.
```{r}
density_f = function(x) {
  if(abs(x) <= 1) {
    return(1-abs(x))
  } else {
    return(0)
  }
}

plot(density_f, xlim = c(-1,1))

```


