---
title: "stat430 hw11"
author: "Nora Garrity- ngarri3"
date: "12/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
Figshare.file <- read.csv("~/Downloads/Figshare file.csv")
test.group = Figshare.file[8:13]
log.test.group = log(test.group)
control.group = Figshare.file[14:19]
log.control.group = log(control.group)
```

**Problem 1** two- tailed signed- rank Wilcoxon test
```{r}
wilcox.test(as.numeric(unlist((log.test.group)), as.numeric(unlist(log.control.group), paired = TRUE)))
```
Ho is rejected due to this very low p value, meaning that the control group and the vaccine group do not follow the same distribution as each other, thus varifying the researches conclusion.


**Problem 2** Mann- Whitney U test
```{r}
wilcox.test(as.numeric(unlist((log.test.group)), as.numeric(unlist(log.control.group), paired = FALSE)))
```
Again, Ho is rejected due to this very low p value, meaning that the control group and the vaccine group do not follow the same distribution as each other, thus varifying the researches conclusion.


